Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/example_domains.tex

% Description of visuals.
In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In some abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were not labelled).

@@

Minefield is a slight variant of Grid World. The transitions and rewards are perturbed, and there is no down action available to the agent. There is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right. The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$. We visualize the original Minefield, represented as a graph, and the abstract Minefield in ~\ref{ref:minefield-visual}.

>>>>

% Description of visuals.
We provide graphical visuals of both ground $\acp{MDP}$ and resulting abstract $\acp{MDP}$. In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In some abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were not labelled).

@@

Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $.2$.  The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$. We visualize the original Minefield and the abstract Minefield in ~\ref{ref:minefield-visual}.
